---
title: "tast_2"
author: "praveen"
date: "9/11/2021"
output: html_document
---

                            THE SPARKS FOUNDATION GRIP PROGRAM(APRIL-2021)
                           DATA SCIENCE AND BUISNESS ANALYTICS INTERNSHIP
### TASK-2:FROM THE GIVEN "IRIS" DATASET PREDICT THE OPTIMUM NUMBER OF CLUSTER AND REPRESENT IT VISUALLY                           
BY: PRAVEEN S
  
  
  
### importing the dataset

```{r,results='hide'}
datasets::iris
```

### installing packages
```{r,message=TRUE,warning=TRUE,message=FALSE,warning=FALSE}
library("tidyverse")       
library("cluster")         
library("reshape")
library("ggplot2")
```



### Exploring the Data set
```{r}
mydata <- iris
```

```{r}
head(mydata)
```


## visualizing the dataset
### Let’s visualize the data now with ggplot2

### Sepal-Length vs. Sepal-Width
```{r}
ggplot(mydata)+geom_point(aes(x = Sepal.Length, y = Sepal.Width), stroke = 2)+facet_wrap(~ Species)+labs(x = 'Sepal Length', y = 'Sepal Width')+theme_linedraw()
```

### Petal-Length vs. Petal-Width
```{r}
ggplot(mydata)+geom_point(aes(x = Petal.Length, y = Petal.Width), stroke = 2)+facet_wrap(~ Species)+ labs(x = 'Petal Length', y = 'Petal Width')+theme_gray()
```



### Sepal-Length vs. Petal-Length
```{r}
ggplot(mydata)+geom_point(aes(x = Sepal.Length, y = Petal.Length), stroke = 2)+facet_wrap(~ Species)+ labs(x = 'Sepal Length', y = 'Petal Length')+ theme_bw()
```



### Sepal-Width vs. Pedal-Width
```{r}
ggplot(mydata)+geom_point(aes(x = Sepal.Width, y = Petal.Width), stroke = 2)+ facet_wrap(~ Species)+ labs(x = 'Sepal Width', y = 'Pedal Width')+theme_bw()
```



## Box plots

### sepal.length
```{r}
ggplot(mydata)+geom_boxplot(aes(x = Species, y = Sepal.Length, fill = Species))+theme_bw()
```



### sepal.width

```{r}
ggplot(mydata)+geom_boxplot(aes(x = Species, y = Sepal.Width, fill = Species))+theme_bw()

```


### petal.length

```{r}
ggplot(mydata)+geom_boxplot(aes(x = Species, y = Petal.Length, fill = Species))+theme_bw()

```


### petal.width

```{r}
ggplot(mydata)+geom_boxplot(aes(x = Species, y = Petal.Width, fill = Species))+theme_bw()

```



## k-means Clustering

### Find the optimal number of clusters by Elbow Method

```{r}
set.seed(123)
wcss <- vector()
for (i in 1:10) wcss[i] <- sum(kmeans(mydata[, -5], i)$withinss)
plot(1:10, wcss, type = 'b',  main = paste('The Elbow Method'),xlab = 'Number of Clusters',ylab = 'WCSS')
```

### the elbow point : k(centers) = 3



### Apply kmeans function to the feature columns

```{r}
set.seed(123)
km <- kmeans( x = mydata[, -5] , centers = 3)

yclus <- km$cluster
table(yclus)
```


### Visualize the kmeans clusters

```{r}
clusplot(mydata[, -5], yclus, lines = 0,shade = TRUE,color = TRUE, labels = 0, plotchar = FALSE, span = TRUE, main = paste('Clusters of Iris Flowers'))

```

### Comparing the clusters

```{r}
mydata$cluster.kmean <- yclus
cm <- table(mydata$Species, mydata$cluster.kmean)
cm
```



### Scatter plots to view Species & kmeans custers

```{r}
mydata$cluster.kmean <- as.factor(mydata$cluster.kmean)

```

### Sepal-Length vs. Sepal-Width (Species)
```{r}
ggplot(mydata)+geom_point(aes(x = Sepal.Length, y = Sepal.Width, color = Species) , size = 10)+ labs(x = 'Sepal Length', y = 'Sepal Width')+ggtitle("Species")+theme_bw()
```



### Sepal-Length vs. Sepal-Width (kmeans cluster)
```{r}
ggplot(mydata)+geom_point(aes(x = Sepal.Length, y = Sepal.Width,  color = cluster.kmean) , size = 10)+ labs(x = 'Sepal Length', y = 'Sepal Width')+ggtitle("kmeans Cluster")+theme_bw()

```


### Petal-Length vs. Petal-Width (Species)
```{r}
ggplot(mydata)+geom_point(aes(x = Petal.Length, y = Petal.Width,color = Species) , size = 10)+ labs(x = 'Petal Length', y = 'Petal Width')+ggtitle("Species")+theme_bw()
```


### Petal-Length vs. Petal-Width (kmeans cluster)
```{r}
ggplot(mydata)+ geom_point(aes(x = Petal.Length, y = Petal.Width, color = cluster.kmean) , size = 10)+   labs(x = 'Petal Length', y = 'Petal Width')+ ggtitle("kmeans Cluster")+theme_bw()
```












